\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-07 Manuscript/reply.tex
minor

\usepackage[dvipsnames]{color}
\definecolor{darkblue}{rgb}{0.1, 0.2, 0.6}

\newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
\newcommand{\of}[1]{\textcolor{green}{(MC: #1)}}

@@

\begin{center}
  {\Large\bf Response to the Comments}
\end{center}

@@

\jy{What is ``the first point?''  Please quote everything from the
  reviewer, including the positive comments.}
\of{resolved}

@@

Thank you for these encouraging comments.

>>>>

\usepackage[dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.1, 0.2, 0.6}

\newcommand{\jy}[1]{\textcolor{orange}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
\newcommand{\of}[1]{\textcolor{purple}{(OF: #1)}}

@@

\begin{center}
  {\Large\bf TAS-23-296: Response to the Comments}
\end{center}

@@

@@

We thank the reviewer for the accurate summary of our contributions
and these encouraging comments.
